Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2013-01-14 chi2013-webbox.tex
abstract short
Refs \small
foo

\section{Introduction}
In recent years, an unprecedented quantity and variety of information has been made available as structured data on the Web.  The explosion of structured data APIs and downloadable data sets has arrived from many different sectors, including retail, banking, social networking, opinion and recommendation sites, mobile and desktop apps, as well as from new kinds sensors and devices such as wearable activity and bio-sensors. Beyond commercial apps and services, governments have embraced releasing data as a way of providing transparency and accountability to their citizens, causing a huge push to release ``open data'' to the public, at scales ranging from the smallest local councils to entire national departments.

@@

\section{Background}
Our work has been informed by three fields of inquiry, comprising PIM, database integration, and end-user mashups and toolkits.  Our primary motivation stems from field studies in PIM, where the need for consolidating data has been observed. This is an area in which many challenges remain, however, specifically, in reconciling the differences that arise among representations when data is created by different people, at different times, and for different purposes. As described by Alon Halevy:

@@

DataPalette's approach exhibits similarities with the user-driven methods just mentioned, in that the user performs data reconciliation using concrete instances as examples, but also avoids the need for any sort of programming.  Previous systems utilising this approach have included ``Cards, Relations and Templates'' \cite{Dontcheva:2007:RCS:1294211.1294224} and Potluck \cite{citeulike:3875264} both of which permit the user to reconcile instances from different schemas into a uniform representation using drag-and-drop gestures to specify relations among fields.  \emph{DataPalette} extends this approach to a data workbench environment which allows people to easily consolidate and compare instances by their properties.

@@

In the first of two pre-studies, we aimed to get an updated understanding of the use of multiple information sources in information gathering on the Web. Several basic questions drove our inquiry.  First, were people increasingly relying only on a handful of ``super-sites'' (Facebook, Wikipedia), or searching across distributed sources of information?  If the former were true, merely integrating PIM tools with the small number of super-sites would provide greater benefit than tackling the more challenging problem of integrating data from an array of arbitrary sources on the Web.  In a related vein, why did some people choose a single source for information gathering, while others selected multiple sources?  What advantages were gained in consulting multiple sources?

@@

The 8 participants, recruited informally via word of mouth, consisted of 7 males and 1 female. They were split evenly into two age groups of 18--25 and 26--32.   
% mention # that were computer scientists here?

%\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported regular usage of multiple websites to accomplish tasks, examples of which included: shopping (food, consumer electronics, hotels and flights), choosing a restaurant, job-seeking, selecting a university, seeking a recipe, or finding answers to technical problems.  When initiating a task, it was common for participants to use Google to discover several related websites, which would then be explored in different ways, depending on the task at hand. For shopping-oriented tasks, a balance of price, quality of merchandise, and speed of delivery was sought.  For product reviews, single sources alone were not trusted due to possible biases, or incomplete coverage of products' desired features.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To benefit from the fullest coverage of information, many different websites of different types were consulted, such as manufacturers' websites for technical details, and review aggregates for a range of opinions.

@@

To remain consistent with the drag-and-drop interactions used throughout the interface, we introduced the ability to simply drag one instance directly on top of another, to specify that these two items should be combined.  This action also caused the \emph{same-as display} in the lower left of the screen to indicate this new combined relationship.  The display also acted as a mechanism to delete/undo combinations, which reverted representations of instances back to their original, separate forms. An illustration of this interaction is provided in Figure \ref{fig:sameas}.  Since individually dragging and dropping items could be tedious for large groups of items, we extended this to allow entire groups to be dropped on to other groups.  DP would then identify matching pairs among items in the dragged and target groups by comparing the labels of items in each group, respectively.  Only exact matches (excepting white space and underscores) were considered to correspond to label matches, and these were automatically combined.  The rest were added to the target group as distinct elements, which could be manually combined by hand.\looseness=-1

@@

% If you want to use smaller typesetting for the reference list,
% uncomment the following line:
% \small
\bibliographystyle{acm-sigchi}
\bibliography{carpedata}
\end{document}

>>>>

\section{Introduction}
In recent years, an unprecedented quantity and variety of information has been made available as structured data on the Web.  The explosion of structured data APIs and downloadable data sets has arrived from many different sectors, including retail, banking, social networking, opinion and recommendation sites, mobile and desktop apps, as well as from new kinds of sensors and devices such as wearable activity and bio-sensors. Beyond commercial apps and services, governments have embraced releasing data as a way of providing transparency and accountability to their citizens, causing a huge push to release ``open data'' to the public, at scales ranging from the smallest local councils to entire national departments.

@@

\section{Background}
Our work has been informed by three fields of inquiry, comprising PIM, database integration, and end-user mashups and toolkits.  Our primary motivation stems from field studies in PIM, where the need for consolidating data has been observed. This is an area in which many challenges remain, specifically, in reconciling the differences that arise among representations when data is created by different people, at different times, and for different purposes. As described by Alon Halevy:

@@

DataPalette's approach exhibits similarities with the user-driven methods just mentioned, in that the user performs data reconciliation using concrete instances as examples, but also avoids the need for any sort of programming.  Previous systems utilising this approach have included ``Cards, Relations and Templates'' \cite{Dontcheva:2007:RCS:1294211.1294224} and Potluck \cite{citeulike:3875264} both of which permit the user to reconcile instances from different schemas into a uniform representation using drag-and-drop gestures to specify relations among fields.  DataPalette extends this approach to a data workbench environment which allows people to easily consolidate and compare instances by their properties.

@@

In the first pre-study, we aimed to get an updated understanding of the use of multiple information sources in information gathering on the Web. Several basic questions drove our inquiry.  First, were people increasingly relying only on a handful of ``super-sites'' (Facebook, Wikipedia), or searching across distributed sources of information?  If the former were true, merely integrating PIM tools with the small number of super-sites would provide greater benefit than tackling the more challenging problem of integrating data from an array of arbitrary sources on the Web.  In a related vein, why did some people choose a single source for information gathering, while others selected multiple sources?  What advantages were gained in consulting multiple sources?

@@

The 8 participants, recruited informally via word of mouth, consisted of 7 males and 1 female, ranging in ages of 18--32.   
% mention # that were computer scientists here?

%\subsubsection{Question 1: Heterogenous Data Tasks}
All participants reported regular usage of multiple websites to accomplish tasks, examples of which included: shopping, choosing a restaurant, job-seeking, selecting a university, seeking a recipe, or finding answers to technical problems.  When initiating a task, it was common for participants to use Google to discover several related websites, which would then be explored in different ways, depending on the task at hand. For shopping-oriented tasks, a balance of price, quality of merchandise, and speed of delivery was sought.  For product reviews, single sources alone were not trusted due to possible biases, or incomplete coverage of products' desired features.  
% Jim - Not sure if this is relevant. If it is, put it back in.
% one participant said that video reviews of items were particularly helpful, as the aesthetics and scale of the item could be seen.
% Social networks were identified to have different functions, such as different groups of people belong to each and share different types of opinions.  One participant said that they shared their outlook and gmail calendars, but only for work events and did not record social activities on them.
To benefit from the fullest coverage of information, many different websites of different types were consulted, such as manufacturers' websites for technical details, and review aggregates for a range of opinions.

@@

To remain consistent with the drag-and-drop interactions used throughout the interface, we introduced the ability to simply drag one instance directly on top of another, to specify that these two items should be combined.  This action also caused the \emph{Same-As display} in the lower left of the screen to indicate this new combined relationship.  The display also acted as a mechanism to delete/undo combinations, which reverted representations of instances back to their original, separate forms. An illustration of this interaction is provided in Figure \ref{fig:sameas}.  Since individually dragging and dropping items could be tedious for large groups of items, we extended this to allow entire groups to be dropped on to other groups.  DP would then identify matching pairs among items in the dragged and target groups by comparing the labels of items in each group, respectively.  Only exact matches (excepting white space and underscores) were considered to correspond to label matches, and these were automatically combined.  The rest were added to the target group as distinct elements, which could be manually combined by hand.\looseness=-1

@@

% If you want to use smaller typesetting for the reference list,
% uncomment the following line:
\small
\bibliographystyle{acm-sigchi}
\bibliography{carpedata}
\end{document}
